Visualization of [fulle name] Fractional Integrals

### 2019-05-22 fractional/CMJ style files/article-template.tex
finished geo section

\noindent
There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
having to sum together the area of multiple rectangular integration strips. Moreover, the shape of the non-rectangular integration strips we should use is determined by the function $a(y)$. We can express this notion more formally as 
follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
We are now able to construct the following sum (the lower Cavalieri sum):
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
the Cavalieri integral:
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
integral by using the transformation functions $h$ and $g$. Expressed mathematically:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
\end{equation}
We can calculate $g$ as follows:
\begin{equation}
g(x) = x - a\circ f(x) + a.
\end{equation}
Moreover, $h=g^{-1}$. We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
If we use its Riemann equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
\end{equation}
If we use its Riemann-Stieltjes equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}

@@

\noindent
Since, Eq.~\eqref{eq:cav} is a Cavalieri integral it has a clear geometric interpretation (see Fig.~\ref{fig:caval2}). The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
by summing together the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of theses integration 
strips will change if either $\alpha$ or $t$ is changed. If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).

Furthermore, Eq.~\eqref{??} implies that we can use $h_t^{\alpha}(x)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
\begin{equation}
\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}
We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{} or we can evaluate Eq.~\eqref{}.

>>>>

\noindent
There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
having to sum together the area of multiple rectangular integration strips. Moreover, the shape of the non-rectangular integration strips we should use is determined by the function $a(y)$. We can express this notion more formally as 
follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
We are now able to construct the following sum (the lower Cavalieri sum):
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
the Cavalieri integral:
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
integral by using the transformation functions $h$ and $g$. Expressed mathematically:
\begin{equation}
\label{eq:main_cav}
\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
\end{equation}
We can calculate $g$ as follows:
\begin{equation}
g(x) = x - a\circ f(x) + a.
\end{equation}
Moreover, $h=g^{-1}$. We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
If we use its Riemann equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
\end{equation}
If we use its Riemann-Stieltjes equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}

@@

\noindent
We can easily assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2}). The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$. If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\

\noindent
Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
\begin{equation}
\label{eq:option2}
\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}
We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
